---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require(codecheck)
require(knitr)
require(rprojroot)
require(yaml)
require(xtable)
require(tibble)
require(readr)
options(width=60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

This workflow was very straightforward to check following the authors' README. All figures stored in the repository could be recreated and match the ones given in the manuscript.

# CODECHECKER notes

```{r git_sha, echo=FALSE}
gitInfo <- ""
if(git2r::in_repository(root)) {
  gitInfo <- paste0("This evaluation is based on the commit `", git2r::last_commit()$sha, "`")
}
```

I forked the [GitHub repo provided by the authors](https://github.com/rsbivand/LICD_article) into the codecheckers organisation: [codecheckers/LICD_article](https://github.com/codecheckers/LICD_article). `r gitInfo`.
The authors deposited the contents of the repository on Zenodo at [https://doi.org/10.5281/zenodo.4283766](https://doi.org/10.5281/zenodo.4283766).

The repository contains some R code and a number of `.jpeg` files.
Data is downloaded as part of the scripts.

I went through the steps in the README, and only had to install a few packages that were not available on my system yet.
Using the provided `DESCRIPTION` file, I installed dependencies with `devtools::install_deps()`.
<!--Remotes: r-spatial/mapview@7d097bc2928fe5d5be676d30956c62e98952260f-->
Thanks to the solid documentation within the scripts and the readable code, I also knew to use the development version of the package `mapview`.

This took around 25 minutes to complete on my laptop (8 cores, 40 GB RAM, SSD).
From the diff between the captures outputs, it's quite easy to see the differences in the computing environments, but that no relevant problems occurred during execution.
I briefly confirmed the workflow also runs in an `rocker/geospatial:4.0.3` container.

## Recommendations to authors

The code was well documented and worked flawlessly on my local machine, there are a few things the authors could consider for their next workflow publication, some of which the authors already picked up in a revision of their repository.

- (authors added `DESCRIPTION` file) use `renv` package or a `DESCRIPTION` file to define the dependencies (= use R package structure)
- (authors updated README) document in README that development version of package `mapview` is needed
- (authors updated README) the interactive map is a bonus compared to the paper - mention how to get to it in the README (the `.zip` file)
- (authors created Zenodo record) deposit a copy of your repo on Zenodo to make the workflow citable and archived
- The data could possibly be republished with the workflow just to be sure, since it is available under open licenses; I can't judge the long term availability of the used download URLs

\clearpage

# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for(i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i,"dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", "Test ", "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently reproduce the results of a computational analysis given the data and code from a third party.
A CODECHECK does not check whether the original computation analysis is correct.
However, as all materials required for the reproduction are freely available by following the links in this document, the reader can then study for themselves the code and data.

# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
